Zero-shot task adaptation by homoiconic meta-mapping

### 2019-09-12 writing/homoiconic_meta_mapping_main.tex
Some small tweaks, starting to switch to ICLR format

\PassOptionsToPackage{numbers}{natbib}

\usepackage[preprint]{neurips_2019}

@@

\setcitestyle{square}

\begin{document}
\title{Zero-shot task adaptation by homoiconic meta-mapping}
\author{%
Andrew K. Lampinen\\
Department of Psychology\\
Stanford University\\
\texttt{lampinen@stanford.edu}\\
\And
James L. McClelland\\
Department of Psychology\\
Stanford University\\
\texttt{mcclelland@stanford.edu}\\
}
\date{}
\maketitle

@@

\vspace{-0.75em} % section
\section{Introduction}
\vspace{-0.5em} % section
Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep{Lake2016, Marcus2018}. One fundamental reason for this is that humans are aware of what we are trying to compute and why. By contrast, there is a fundamental separation of knowledge within most deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between data and tasks. That is, a neural network's knowledge about what is being computed is only implicitly accessible to those computations. \par
\looseness=-1
There are a number of advantages to representing knowledge about data and tasks together. In particular, it can grant the ability to rapidly adapt behavior to a new task. The problem of rapid learning has been partially addressed by meta-learning systems \citep[see also section \ref{sec_discussion}]{Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}. However, humans can use our knowledge of a task to flexibly alter our behavior in accordance with a change in task demands or a single instruction. For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance without any retraining (i.e. zero-shot). Deep learning systems at present generally lack this representational flexibility. \par
In this paper, we propose a new class of tasks based on this idea: meta-mappings, i.e. mappings between tasks (see below). This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models. To address this challenge, we propose using architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity. (A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.) By treating both data and task behaviors as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable. This yields the ability to not only learn to solve new tasks, but to learn how to transform these solutions in response to changing task demands. We demonstrate that our architectures can flexibly remap their behavior to address the meta-mapping challenge. By allowing the network to recursively treat its task representations as data points, and transform them to produce new task representations, our approach is able to achieve this flexibility parsimoniously. We suggest that approaches like ours will be key to building more intelligent and flexible deep learning systems. \par

\vspace{-0.25em}
\section{Meta-mapping}
\vspace{-0.5em} % section
%Can cut "the task"s in go sentence if needed
We propose the meta-mapping challenge. We define a meta-mapping as a task, or mapping, that takes a task as an input, output, or both. These include mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior). While the first two categories have been partially addressed in prior work \citep[e.g.][]{Hermann2017, Co-Reyes2019}, the latter is more novel. (We discuss the relationship between our work and prior work in section \ref{sec_discussion}.) This adaptation can be cued in several ways, including examples of the mapping (after winning and losing at poker, try to lose at blackjack) or natural-language instructions (``try to lose at blackjack''). \par
We argue that task-to-task meta-mappings are a useful way to think about human-like flexibility, because a great deal of our rapid adaptation is from a task to some variation on that task. For example, the task of playing go on a large board is closely related to the task of playing go on a small board. Humans can exploit this to immediately play well on a different board, but deep learning models generally have no way to achieve this. We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to lose, or trying to achieve some orthogonal goal. While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not fully capture human flexibility. Given appropriate conditioning (see below), our architecture can adapt to substantial task alterations zero-shot, that is, without seeing a single example from the new task \citep{Lake2016}. We suggest that meta-mappings offer a way to understand this flexibility, and a way for deep-learning models to achieve it. Achieving the flexibility to adapt to meta-map to new tasks will be an important step toward more general intelligence -- intelligence that is not limited to precisely the training domains it has seen. \par

\vspace{-0.25em}
\section{Homoiconic meta-mapping (HoMM) architecture}
\vspace{-0.5em} % section
To address these challenges, we propose HoMM architectures, composed of two components: 
\vspace{-1em}
\begin{enumerate} \setlength \itemsep{0em}
\item Input/output systems: domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
\item A meta-learning system that a) learns to embed tasks into the shared embedding space $Z$, b) learns to use these task embeddings to perform task-appropriate behavior, c) learns to embed meta-mappings into the same space, and d) learns to use these meta-mapping embeddings to transform basic task embeddings in a meta-mapping appropriate way.\end{enumerate}
\vspace{-0.75em}
\looseness=-1
These architectures are homoiconic because they have a completely shared $Z$ for individual data points, tasks, and meta-mappings. Why is this useful? The primary advantage is that it parsimoniously allows for arbitrary mappings between these entities. In addition to basic tasks, the system can learn to perform meta-mappings to follow instructions or change behavior. That is, it can transform task representations using the same components it uses to transform basic data points. (See also appendix \ref{app_lesion_results_shared_z}.) \par
Without training on meta-mappings, of course, the system will not be able to execute them well. However, as we will show, if it is trained on a broad enough set of such mappings, it will be able to generalize to new instances drawn from the same meta-mapping distribution. For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however. This reflects the structure of human behavior -- we are able to adapt rapidly when new knowledge is relatively consistent with our prior knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow \citep[cf.][]{Kumaran2016, Botvinick2019}. \par 
\begin{figure}
\centering
\begin{tikzpicture}[scale=0.8, every node/.style={scale=0.8}]
%% basic meta learning
\begin{scope}[shift={(0.4, 0.4)}]
\draw[boundingbox, fill=white] (-3, -4.3) rectangle (2.5, 3.2);
\end{scope}
\begin{scope}[shift={(0.2, 0.2)}]
\draw[boundingbox, fill=white] (-3, -4.3) rectangle (2.5, 3.2);
\end{scope}

@@

\vspace{-0.5em}
\paragraph{Basic meta-learning:} To perform a basic task, input and target encoders ($\mathcal{I}$ and $\mathcal{T}$) are used to embed individual pairs from an example dataset \(D_1\), to form a dataset of example (input, output) tuples (fig. \ref{architecture_inference_fig}a). These examples are fed to $\mathcal{M}$, which produces a function embedding (via a deep neural network, including an element-wise max across the examples). This function embedding is mapped through they hyper network $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a dataset of embedded probe inputs, and $\mathcal{O}$ to map the resultant embeddings to outputs. This system can be trained end-to-end on target outputs for the probes. Having two distinct datasets forces generalization at the meta-learning level, see appendix \ref{app_clarifying_holdouts}. See appendix \ref{app_model_details} for detailed architecture, and hyper-parameters. \par 

@@

%\subsection{Boolean functions}
%As a proof of concept, we first evaluated the system on a simple task of computing boolean functions on boolean inputs. Specifically, we can imagine mapping from binary-valued input vectors to a single binary output representing the evaluation of some logical proposition on the input. We train the system to figure out how to compute the predicate from seeing a subset of the (input, output) pairs. \par   
%We can then train the system to do various meta-mappings, for example identifying certain types of functions (like XOR) or negating predicates. \par
%
\section{Learning multivariate polynomials} \label{sec_poly}
\vspace{-0.5em} % section
\begin{figure}
\centering
\begin{subfigure}[t]{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/poly/basic_results.png}
\caption{The polynomials domain, section \ref{sec_poly}.}
\label{poly_basic_results}
\end{subfigure}%
\begin{subfigure}[t]{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/basic_meta_learning.png}
\caption{The cards domain, section \ref{sec_cards}.}
\label{cards_basic_results}
\end{subfigure}%
\caption{The HoMM system succeeds at the basic meta-learning tasks, which are a necessary prerequisite for meta-mappings. (\subref{poly_basic_results}) Basic meta-learning in the polynomials domain, section \ref{sec_poly}. The system successfully generalizes to held out polynomials. The solid line indicates optimal performance; the dashed line indicates untrained model performance. (\subref{cards_basic_results}) Basic meta-learning in the cards domain, section \ref{sec_cards}. The system successfully generalizes to held out games, both when trained on a random sample of half the tasks, or when a targeted subset is held out. The gray dashed line indicates chance performance, while the solid lines are optimal performance. The orange dashed lines show how well the system could perform by playing the strategy from the most correlated trained task. The fact that it generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing a few strategies and picking the closest. Error-bars throughout are bootstrap 95\%-confidence intervals, numerical values for plots can be found in appendix \ref{app_numerical_results}.}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/poly/meta_results.png}
\caption{The polynomials domain, section \ref{sec_poly}.}
\label{poly_meta_map_results_examples}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/meta_mapping.png}
\caption{The cards domain, section \ref{sec_cards}.}
\label{cards_meta_map_results_examples}
\end{subfigure}%
\caption{The HoMM architecture performs well at meta-mappings. (\subref{poly_meta_map_results_examples}) The system generalizes to apply learned meta-mappings to new polynomials, and to apply unlearned meta-mappings. The plots show the loss produced when evaluating the mapped embedding on the target task. For example, if the initial polynomial is $p(x) = x + 1$, and the meta-task is ``square,'' the loss would be evaluated by applying this meta-mapping to the embedding of $p(x)$ and evaluating how well the function specified by the mapped embedding regresses $p(x)^2 = x^2 + 2x + 1$. The solid line indicates optimal performance; the dashed line is untrained model performance.
(\subref{cards_meta_map_results_examples}) The system generalizes to meta-mapping new tasks in the cards domain. The system is trained to do the meta-mappings shown here on a subset of its basic tasks, and is able to generalize these mappings to perform novel tasks it has not been trained on. For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants. When given a held-out game, it is able to apply the mapping to guess how to play the losing variation. This plot shows the reward produced by taking the mapped embedding and playing the targeted game. The gray dashed line indicates random performance, while the colored dashed lines indicate performance if the system did not alter its behavior in response to the meta-mapping. The system generally exceeds these baselines, although the switch-suits baseline is more difficult with the targeted holdout. 
Error-bars are bootstrap 95\%-CIs.} 
\label{meta_map_results}
\end{figure}

%% Cut example if necessary
As a proof of concept, we first evaluated the system on the task of learning polynomials of degree $\leq 2$ in 4 variables (i.e. the task was to regress functions of the form $p: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $p \in \mathcal{P}_2 \left(\mathbb{R}\right)$, though the model was given no prior inductive bias toward polynomial forms). For example, if $p(w,x,y,z) = x$, the model might see examples like $(-1,1,1,1; 1)$ and $(0.7, 2.1, 1.3, -4; 2.1)$, and be evaluated on its output for points like $(-1, -1.3, 0.5, 0.3)$. This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying polynomials by a constant, squaring them, or permuting their input variables). This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks. Details of the architecture and training can be found in appendix \ref{app_detailed_methods}.\par
\vspace{-0.7em}
\paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in fig. \ref{poly_basic_results} (with good sample-efficiency, see supp. fig. \ref{supp_poly_sweep_results}). \par 
\vspace{-0.7em}
\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior (fig. \ref{poly_meta_map_results_examples}). We train the system to perform a variety of mappings, for example switch the first two inputs of the polynomial, add 3 to the polynomial, or square the polynomial. We then test its ability to generalize to held-out mappings, for example a held-out input permutation, or an unseen additive shift. The system is both able to apply learned meta-mappings to held-out tasks, and to apply meta-mappings it has not been trained on, simply by seeing examples of the mapping. \par

@@

\vspace{-0.5em} % section

@@

\vspace{-0.7em}

@@

\vspace{-0.5em}

@@

 \vspace{-1em}

@@

\subsubsection*{Acknowledgements}
We would like to acknowledge Noah Goodman, Surya Ganguli, Katherine Hermann, Erin Bennett, and Arianna Yuan for stimulating questions and suggestions on this project.

\bibliographystyle{acm}
\bibliography{arrr}

>>>>

%\PassOptionsToPackage{numbers}{natbib}

%\usepackage{neurips_2019}
\usepackage{iclr2020_conference,times}

@@

%\setcitestyle{square}

%\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.
\begin{document}
\title{Zero-shot task adaptation by homoiconic meta-mapping}
\author{%
Andrew K. Lampinen\\
Department of Psychology\\
Stanford University\\
\texttt{lampinen@stanford.edu}\\
\And
James L. McClelland\\
Department of Psychology\\
Stanford University\\
\texttt{mcclelland@stanford.edu}\\
}
\date{}
\maketitle

@@

%\vspace{-0.75em} % section
\section{Introduction}
%\vspace{-0.5em} % section
Humans are able to use and reuse knowledge more flexibly than most deep learning models can \citep{Lake2016, Marcus2018}. One fundamental reason for this is that humans are aware of what we are trying to compute and why. By contrast, there is a fundamental separation of knowledge within most deep neural networks -- although deep networks represent knowledge about data (in their activations) and knowledge about the structure of tasks (in their parameters), they do not represent any relationships between data and tasks. That is, a neural network's knowledge about what is being computed is only implicitly accessible to those computations. \par
\looseness=-1
There are a number of advantages to representing knowledge about data and tasks together. In particular, it can grant the ability to rapidly adapt behavior to a new task. The problem of rapid learning has been partially addressed by meta-learning systems \citep[see also section \ref{sec_discussion}]{Santoro2016, Finn2017a, Finn2018, Stadie2018, Botvinick2019}. However, humans can use our knowledge of a task to flexibly alter our behavior in accordance with a change in task demands or a single instruction. For example, once we learn to play a game, we can immediately switch to playing in order to lose, and can achieve reasonable performance without any retraining (i.e. zero-shot). Deep learning systems at present generally lack this representational flexibility. \par
In this paper, we propose a new class of tasks based on this idea: meta-mappings, i.e. mappings between tasks (see below). This type of transfer is easily accessible to humans \citep{Lake2016}, but is generally inaccessible to most deep-learning models. To address this challenge, we propose using architectures which essentially take a functional perspective on meta-learning, and exploit the idea of homoiconicity. (A homoiconic programming language is one in which programs in the language can be manipulated by programs in the language, just as data can.) By treating both data and task behaviors as functions, we can conceptually think of both data \emph{and} learned task behaviors as transformable. This yields the ability to not only learn to solve new tasks, but to learn how to transform these solutions in response to changing task demands. We demonstrate that our architectures can flexibly remap their behavior to address the meta-mapping challenge. By allowing the network to recursively treat its task representations as data points, and transform them to produce new task representations, our approach is able to achieve this flexibility parsimoniously. We suggest that approaches like ours will be key to building more intelligent and flexible deep learning systems. \par

%\vspace{-0.25em}
\section{Meta-mapping}
%\vspace{-0.5em} % section
%Can cut "the task"s in go sentence if needed
We propose the meta-mapping challenge. We define a meta-mapping as a task, or mapping, that takes a task as an input, output, or both. These include mapping from tasks to language (explaining), mapping from language to tasks (following instructions), and mapping from tasks to tasks (adapting behavior). While the first two categories have been partially addressed in prior work \citep[e.g.][]{Hermann2017, Co-Reyes2019}, the latter is more novel. (We discuss the relationship between our work and prior work in section \ref{sec_discussion}.) This adaptation can be cued in several ways, including examples of the mapping (after winning and losing at poker, try to lose at blackjack) or natural-language instructions (``try to lose at blackjack''). \par
We argue that task-to-task meta-mappings are a useful way to think about human-like flexibility, because a great deal of our rapid adaptation is from a task to some variation on that task. For example, the task of playing go on a large board is closely related to the task of playing go on a small board. Humans can exploit this to immediately play well on a different board, but deep learning models generally have no way to achieve this. We can also adapt in much deeper ways, for example fundamentally altering our value function on a task, such as trying to lose, or trying to achieve some orthogonal goal. While meta-learning systems can rapidly learn a new task from a distribution of tasks they have experience with, this does not fully capture human flexibility. Given appropriate conditioning (see below), our architecture can adapt to substantial task alterations zero-shot, that is, without seeing a single example from the new task \citep{Lake2016}. We suggest that meta-mappings offer a way to understand this flexibility, and a way for deep-learning models to achieve it. Achieving the flexibility to adapt to meta-map to new tasks will be an important step toward more general intelligence -- intelligence that is not limited to precisely the training domains it has seen. \par

%\vspace{-0.25em}
\section{Homoiconic meta-mapping (HoMM) architecture}
%\vspace{-0.5em} % section
To address these challenges, we propose HoMM architectures, composed of two components: 
%\vspace{-1em}
\begin{enumerate} \setlength \itemsep{0em}
\item Input/output systems: domain specific encoders and decoders (vision, language, etc.) that map into a shared embedding space $Z$.
\item A meta-learning system that a) learns to embed tasks into the shared embedding space $Z$, b) learns to use these task embeddings to perform task-appropriate behavior, c) learns to embed meta-mappings into the same space, and d) learns to use these meta-mapping embeddings to transform basic task embeddings in a meta-mapping appropriate way.\end{enumerate}
%\vspace{-0.75em}
\looseness=-1
These architectures are homoiconic because they have a completely shared $Z$ for individual data points, tasks, and meta-mappings. Why is this useful? The primary advantage is that it parsimoniously allows for arbitrary mappings between these entities. In addition to basic tasks, the system can learn to perform meta-mappings to follow instructions or change behavior. That is, it can transform task representations using the same components it uses to transform basic data points. (See also appendix \ref{app_lesion_results_shared_z}.) \par
Without training on meta-mappings, of course, the system will not be able to execute them well. However, as we will show, if it is trained on a broad enough set of such mappings, it will be able to generalize to new instances drawn from the same meta-mapping distribution. For instances that fall outside its data distribution, or for optimal performance, it may require some retraining, however. This reflects the structure of human behavior -- we are able to adapt rapidly when new knowledge is relatively consistent with our prior knowledge, but learning an entirely new paradigm (such as calculus for a new student) can be quite slow \citep[cf.][]{Kumaran2016, Botvinick2019}. \par 
\begin{figure}[t]
\centering
\begin{tikzpicture}[scale=0.8, every node/.style={scale=0.8}]
%% basic meta learning
\begin{scope}[shift={(0.4, 0.4)}]
\draw[boundingbox, fill=white] (-3, -4.3) rectangle (2.5, 3.2);
\end{scope}
\begin{scope}[shift={(0.2, 0.2)}]
\draw[boundingbox, fill=white] (-3, -4.3) rectangle (2.5, 3.2);
\end{scope}

@@

%\vspace{-0.5em}
\paragraph{Basic meta-learning:} To perform a basic task, input and target encoders ($\mathcal{I}$ and $\mathcal{T}$) are used to embed individual pairs from an example dataset \(D_1\), to form a dataset of example (input, output) tuples (fig. \ref{architecture_inference_fig}a). These examples are fed to $\mathcal{M}$, which produces a function embedding (via a deep neural network, including an element-wise max across the examples). This function embedding is mapped through the hyper network $\mathcal{H}$ to parameterize $F$, and then $F$ is used to process a dataset of embedded probe inputs, and $\mathcal{O}$ to map the resultant embeddings to outputs. This system can be trained end-to-end on target outputs for the probes. Having two distinct datasets forces generalization at the meta-learning level, see appendix \ref{app_clarifying_holdouts}. See appendix \ref{app_model_details} for detailed architecture, and hyper-parameters. \par 

@@

%\subsection{Boolean functions}
%As a proof of concept, we first evaluated the system on a simple task of computing boolean functions on boolean inputs. Specifically, we can imagine mapping from binary-valued input vectors to a single binary output representing the evaluation of some logical proposition on the input. We train the system to figure out how to compute the predicate from seeing a subset of the (input, output) pairs. \par   
%We can then train the system to do various meta-mappings, for example identifying certain types of functions (like XOR) or negating predicates. \par
%
\section{Learning multivariate polynomials} \label{sec_poly}
\begin{figure}[t]
\centering
\begin{subfigure}[t]{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/poly/basic_results.png}
\caption{The polynomials domain, section \ref{sec_poly}.}
\label{poly_basic_results}
\end{subfigure}%
\begin{subfigure}[t]{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/basic_meta_learning.png}
\caption{The cards domain, section \ref{sec_cards}.}
\label{cards_basic_results}
\end{subfigure}%
\caption{The HoMM system succeeds at basic meta-learning, which is a necessary prerequisite for meta-mappings. (\subref{poly_basic_results}) The polynomials domain, section \ref{sec_poly}. The system successfully generalizes to held out polynomials. The solid line indicates optimal performance; the dashed line indicates untrained model performance. (\subref{cards_basic_results}) The card games domain, section \ref{sec_cards}. The system successfully generalizes to held out games, both when trained on a random sample of half the tasks, or when a targeted subset is held out. The gray dashed line indicates chance performance, while the solid lines are optimal performance. The orange dashed lines shows performance on held-out tasks of playing the strategy from the most correlated trained task. The fact that the system generally exceeds this difficult baseline shows a deeper form of generalization than just memorizing strategies and picking the closest. Error-bars throughout are bootstrap 95\%-confidence intervals, numerical values for plots can be found in appendix \ref{app_numerical_results}.}
\end{figure}

\begin{figure}[t]
\centering
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/poly/meta_results.png}
\caption{The polynomials domain, section \ref{sec_poly}.}
\label{poly_meta_map_results_examples}
\end{subfigure}%
\begin{subfigure}{0.5\textwidth}
\includegraphics[width=\textwidth]{figures/meta_mapping.png}
\caption{The cards domain, section \ref{sec_cards}.}
\label{cards_meta_map_results_examples}
\end{subfigure}%
\caption{The HoMM architecture performs well at meta-mappings. (\subref{poly_meta_map_results_examples}) The system generalizes to apply learned meta-mappings to new polynomials, and to apply unlearned meta-mappings. The plots show the loss produced when evaluating the mapped embedding on the target task. For example, if the initial polynomial is $p(x) = x + 1$, and the meta-task is ``square,'' the loss would be evaluated by applying this meta-mapping to the embedding of $p(x)$ and evaluating how well the function specified by the mapped embedding regresses $p(x)^2 = x^2 + 2x + 1$. The system succeeds at applying meta-mappings it is trained on to held-out polynomials, as well as applying held-out meta-mappings to either trained or held-out polynomials. The solid line indicates optimal performance; the dashed line is untrained model performance.
(\subref{cards_meta_map_results_examples}) The system generalizes to meta-mapping new tasks in the cards domain. The system is trained to do the meta-mappings shown here on a subset of its basic tasks, and is able to generalize these mappings to perform novel tasks zero-shot. For example, for the ``losers'' mapping, the sytem is trained to map games to their losers variants. When given a held-out game, it is able to apply the mapping to guess how to play the losing variation. This plot shows the reward produced by taking the mapped embedding and playing the targeted game. The gray dashed line indicates random performance, while the colored dashed lines indicate performance if the system did not alter its behavior in response to the meta-mapping. The system generally exceeds these baselines, although the switch-suits baseline is more difficult with the targeted holdout. 
Error-bars are bootstrap 95\%-CIs.} 
\label{meta_map_results}
\end{figure}

As a proof of concept, we first evaluated the system on the task of learning polynomials of degree $\leq 2$ in 4 variables (i.e. the task was to regress functions of the form $p: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $p \in \mathcal{P}_2 \left(\mathbb{R}\right)$, though the model was given no prior inductive bias toward polynomial forms). For example, if $p(w,x,y,z) = x$, the model might see examples like $(-1,1,1,1; 1)$ and $(0.7, 2.1, 1.3, -4; 2.1)$, and be evaluated on its output for points like $(-1, -1.3, 0.5, 0.3)$. This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying polynomials by a constant, squaring them, or permuting their input variables). This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks. Details of the architecture and training can be found in appendix \ref{app_detailed_methods}.\par
%\vspace{-0.7em}
\paragraph{Basic meta-learning:} First, we show that the system is able to achieve the basic goal of learning a held-out polynomial from a few data points in fig. \ref{poly_basic_results} (with good sample-efficiency, see supp. fig. \ref{supp_poly_sweep_results}). \par 
%\vspace{-0.7em}
\paragraph{Meta-mapping (task $\rightarrow$ task):} Furthermore, the system is able to perform meta-mappings over polynomials in order to flexibly reconfigure its behavior (fig. \ref{poly_meta_map_results_examples}). We train the system to perform a variety of mappings, for example switch the first two inputs of the polynomial, add 3 to the polynomial, or square the polynomial. We then test its ability to generalize to held-out mappings, for example a held-out input permutation, or an unseen additive shift. The system is both able to apply learned meta-mappings to held-out basic tasks, and to apply held-out meta-mappings it has not been trained on, simply by seeing examples of the mapping. \par

@@

%\vspace{-0.5em} % section

@@

%\vspace{-0.7em}

@@

%\vspace{-0.5em}

@@

% \vspace{-1em}

@@

%\subsubsection*{Acknowledgements}
%We would like to acknowledge Noah Goodman, Surya Ganguli, Katherine Hermann, Erin Bennett, and Arianna Yuan for stimulating questions and suggestions on this project.

\bibliographystyle{apalike}
\bibliography{arrr}
